% --- LaTeX CV Template - Lingyun Yang ---

% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings --- %

% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
% \usepackage[dvipsnames]{xcolor}
% \hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Hind links
\hypersetup{hidelinks}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
% \pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{Lingyun Yang}
\hfill{\it\footnotesize Updated \today}}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{8pt}

% --- Contact information and other items --- %

\vspace{0.5cm} 
\begin{center}
\begin{tabular}{lll}
% Line 1: Email, GitHub, LinkedIn
\textbf{Email}: lyangbk@cse.ust.hk &
\hspace{0.25in} \textbf{GitHub}: \href{https://github.com/mental2008}{mental2008} &
\hspace{0.1in} \textbf{LinkedIn}: \href{https://www.linkedin.com/in/lingyun-yang-b2881b18a/}{lingyun-yang-b2881b18a} \\

% Line 2: Phone number, office location, website
\textbf{Phone}: (+852) 9719-0933 & 
\hspace{0.25in} \textbf{Office}: CYT 3007, HKUST & 
\hspace{0.1in} \textbf{Web}: \href{https://www.cse.ust.hk/~lyangbk/}{https://www.cse.ust.hk/$\sim$lyangbk/} \\ 
\end{tabular}
\end{center}

% Set the width of each column
% \begin{longtable}{p{1.3in}p{4.8in}}
\begin{longtable}{p{1in}p{5in}}

% --- Section: Personal profile --- %
{Personal profile}
& Ph.D. Student \\
& Department of Computer Science and Engineering \\
& Hong Kong University of Science and Technology \\
& Clear Water Bay, Kowloon, Hong Kong \\
& \\

% --- Section: Research interests --- %
\nohyphens{Research interests}
& Machine Learning for Systems, Cloud Computing, Resource Management for large-scale GPU Clusters \\
& \\

% --- Section: Education --- %
{Education}
& \textbf{Hong Kong University of Science and Technology (HKUST)} \\
& \textit{Department of Computer Science and Engineering} \\
& Ph.D. in Computer Science and Engineering \hfill 2020 -- Present \\
& $\diamond$ Advisor: Prof. Wei Wang \\
& \\

& \textbf{South China University of Technology (SCUT)} \\
& \textit{School of Computer Science and Engineering} \\
& B.Eng. in Computer Science and Technology \hfill 2016 -- 2020 \\
& $\diamond$ Studied at All-English Innovation Class ({\it GPA: 3.82/4}) \\
& \\

% --- Section: Professional experience ---

{Professional}
& {\textbf{Alibaba Group}} \hfill Hangzhou, China \\
{experience}
& \textit{Research Intern}, Cluster Management Group \hfill Dec. 2020 - Present \\
& $\diamond$ Mentors: Jian He and Dr. Yinghao Yu \\
& $\diamond$ Co-developed Morphling, an open-source auto-configuration framework for machine learning model serving on Kubernetes, with intelligent algorithms to quickly find the optimal configuration. [\href{https://www.cse.ust.hk/~weiwa/papers/morphling-socc21.pdf}{\underline{paper}}][\href{https://kubedl.io/tuning/intro/}{\underline{website}}][\href{https://github.com/kubedl-io/morphling}{\underline{code}}] \\
& \\

& {\textbf{Hong Kong University of Science and Technology}} \hfill Clear Water Bay, Kowloon, Hong Kong \\
& \textit{Research/Teaching Assistant}, System Algorithm Group \hfill Sept. 2020 - Present \\
& \\
 
& {\textbf{Microsoft Research Asia (MSRA)}} \hfill Beijing, China\\
& \textit{Research Intern}, Innovation Engineering Group (IEG) \hfill Jul. 2019 - Jun. 2020 \\
& $\diamond$ Mentors: Lewei Lu and Chong Li \\
& $\diamond$ Applied multiple latest attention mechanisms to face recognition models, integrated with knowledge distillation, built in CNTK. \\
& $\diamond$ Built a neural architecture search pipeline for face recognition tasks. \\
& $\diamond$ Designed a symmetric padding pooling layer with self-attention which can be easily integrated into any model structure, achieve the state-of-the-art performance and improve the robustness to various pertubations. \\
& \\

% --- Section: Publications --- %
\nohyphens{Publications}
& $\diamond$ Luping Wang*, \textbf{Lingyun Yang}*, Yinghao Yu, Wei Wang, Bo Li, Xianchao Sun, Jian He, and Liping Zhang, “Morphling: Fast, Near-Optimal Auto-Configuration for Cloud-Native Model Serving”, to appear in the \textit{Proceedings of ACM Symposium on Cloud Computing} (\textbf{SoCC ’21}), Seattle, WA, November 2021. (*Co-first authors in alphabetical order) \\
& \\

% --- Section: Awards, scholarships, etc. --- %
% --- Note: section title is spread over two lines --- %
{Honors and }
& $\diamond$ Postgraduate Scholarship \hfill 2020 - Present, HKUST \\
{scholarships}
& $\diamond$ Star of Tomorrow Internship Award of Excellence \hfill Jul. 2020, MSRA \\

& $\diamond$ Merit Student \& Excellent Student Cadre \hfill Nov. 2019, SCUT \\
& $\diamond$ National Scholarship \hfill Oct. 2019, China \\

& $\diamond$ Silver Medal, 2019 ICPC China Xi'an National Invitational \hfill May 2019 \\
& $\ \ $ Programming Contest \\

& $\diamond$ First Prize, 17th Guangdong Collegiate Programming Contest \hfill May 2019 \\

& $\diamond$ Silver Medal, 2019 Sanqi Mutual Entertainment Cup \hfill Apr. 2019 \\
& $\ \ $ Programming Contest \\

& $\diamond$ Gold Medal, 2019 South China University of Technology ACM \hfill Apr. 2019 \\
& $\ \ $ Programming Contest \\

& $\diamond$ Bronze Medal, 2018 ACM-ICPC Asia Xuzhou Regional Contest \hfill Oct. 2018 \\

& $\diamond$ Silver Medal, 1st Xiao Mi Collegiate Programming Contest \hfill Sept. 2018 \\

& $\diamond$ Gold Medal, 2018 South China University of Technology ACM \hfill Apr. 2018 \\
& $\ \ $ Programming Contest \\

& $\diamond$ The First Prize Scholarship \hfill Nov. 2017, SCUT \\

& $\diamond$ Bronze Medal, 2017 ACM-ICPC Asia Xian Regional Contest \hfill Oct. 2017 \\

& $\diamond$ Gold Medal, 12th China Youth Robot Competition \hfill Jul. 2012 \\

& $\diamond$ Champion, 2012 RoboCup Youth Robot World Cup China \hfill Mar. 2012 \\
& $\ \ $ Division Selection Competition \\

& \\



% & \textbf{Title of your most recent research paper} \\
% & First author, second author, third author, fourth author. \\
% & \textit{Journal of something or the other, 2020.}\\
% & \\

% & \textbf{Title of your second most recent research paper} \\
% & First author, second author, third author, fourth author. \\
% & \textit{Journal of something or the other, 2020.}\\
% & \\

% & \textbf{Title of your third most recent research paper} \\
% & First author, second author, third author, fourth author. \\
% & \textit{Journal of something or the other, 2020.}\\
% & \\

% --- Section: Teaching activities --- %
\nohyphens{Teaching activities}
& \textbf{Hong Kong University of Science and Technology} \hfill Clear Water Bay, Kowloon, Hong Kong \\
& \textit{Teaching Assistant, Department of Computer Science and Engineering} \\
& $\diamond$ COMP 4651: Cloud Computing and Big Data Systems \hfill Fall 2021 \\
& $\diamond$ COMP 4651: Cloud Computing and Big Data Systems \hfill Spring 2021 \\
& \\

% --- Section: Other experience --- %
{Other}
& \textbf{ACM-ICPC Competition Group} \\
{experience}
& \textit{Group Member \& Team Leader} \hfill 2016 - 2019 \\
& $\diamond$ Coach: Prof. Chuhua Xian \\
& $\diamond$ Major domains: Dynamic Programming, Number Theory, Data Structure, etc. \\

& \textbf{Machine Learning \& Cybernetics Research Group} \\
& \textit{Undergraduate Research Assistant} \hfill 2017 - 2019 \\
& $\diamond$ Advisor: Prof. Patrick Chan \\
& $\diamond$ Completed research projects: Fundus Stitching, Tableware Recognition and NN Visualization. \\

& \textbf{Tencent Innovation Club} \\
& \textit{Vice Chairman} \hfill 2018 - 2019 \\
& $\diamond$ Led the largest student club at the School of Computer Science and Engineering in SCUT, sponsored by Tencent Technology (Shenzhen) CO., LTD. \\

& \textbf{ByteDance Summer Camp} \hfill Beijing, China \\
& \textit{Camper}, Algorithm track \hfill Aug. 2019 \\
& $\diamond$ Mentor: Dr. Yibo Zhu \\
& $\diamond$ Totally 150 participants selected from more than 6k candidates. \\
& $\diamond$ Trained a large scale BERT Model by using Pipeline and Model Parallelism. \\

% International Conference on Machine Learning and Cybernetics, International Conference on Wavelet Analysis and Pattern Recognition
& \textbf{ICMLC \& ICWAPR} \hfill Chengdu, China \\
& \textit{Student helper} \hfill Jul. 2018 \\

& \\

% --- Section: Various skills (programming, software, languages, etc.) ---
\nohyphens{Skills}
& Programming Languages: C++, Python, Golang \\
& Toolkits: Git, \LaTeX, Linux Shell, Qt, MySQL, MarkDown \\
& Languages: English (fluent), Mandarin (Native speaker) \\
& \\

% --- Section: Other interests/hobbies ---

\nohyphens{Miscellaneous}
& Read various kinds of books, play basketball, workout at the gym, food lover. \\
& In my spare time, I also write some blogs about interesting stuffs aperiodically. Here is my personal blog (in Chinese): \href{https://blog.yanglingyun.me/}{https://blog.yanglingyun.me/}. \\

% --- End of CV! --- %

\end{longtable}
\end{document}
